I need a title

### 2018-01-07 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

\begin{document}
\maketitle
\begin{abstract}
I need an abstract

% lncs keyword extension 
\keywords{I, need, keywords}

@@

I need an introduction\ldots{}

\hypertarget{my-approach-i-need-a-section-title}{%
\section{My approach (i need a section
title)}\label{my-approach-i-need-a-section-title}}

\hypertarget{tacit-knowledge-in-elicitation-interviews}{%
\subsection{Tacit knowledge in elicitation
interviews}\label{tacit-knowledge-in-elicitation-interviews}}

Requirements elicitation is the process of finding and formulation
requirements, and this process has many barriers due to stakeholders are
not able to express their needs, explain what they do and why,
conflicting demands, or new demands once other are met{[}1{]}, just to
mention some examples. Many analyst consider interviews the most
important elicitation technique, and usually elicitation process starts
with interviewing the stakeholders. Interviews allow analysts to check
their understanding about the problem domain immediately and ask for
clarifications. Moreover, this technique is versatile in the sense of it
is possible that new and unexpected issues come up and they can be
attacked at that moment.

However, elicit tacit knowledge in interviews is still a hard task to
do. This tacit knowledge can be classified in four groups as describe in
{[}2{]}. The \textbf{known knowns}, \textbf{known unknowns},
\textbf{unknown knowns} and \textbf{unknown unknowns}. The known knowns
is the knowledge that is documented, expressible, and relevant to the
system. In order words, is the scenario in which it is possible to
elicit since the beginning all the requirements, there is no tacit
knowledge. The known unknowns is the knowledge that cannot be
expressible because the stakeholders are not aware of their lack of
domain knowledge, their might forget it. In this case analyst are aware
of the domain knowledge and therefore, their job is to challenge
assumptions or implications. The unknown knowns is the knowledge that
stakeholders hold but it is not documented by some reason. Thus,
analysts should use their interviewing skill to elicit when they spot
any glimpse of that knowledge. The unknown unknowns is the knowledge
that neither the analysts nor stakeholders are aware.

\hypertarget{challenge-tacit-knowledge}{%
\subsection{Challenge tacit knowledge}\label{challenge-tacit-knowledge}}

In the last section we present how to use a theoretical framework based
on arguments and attacks to addresed the different levels of tacit
knowledge. In this section we will compare in which scenario of tacit
knowledge the elicitation interview is more effective based on Aranda et
al.~work {[}4{]} about the effect of domain knowledge on elicitation
process.\\
Effectiveness is described in {[}4{]} as the total percentage of problem
domain elements identified compared to a benchmark. However, since we
have no accesse to any requirement data, we will use the conclusions of
{[}4{]} to compare the different scenarios of tacit knowledge (known
unknowns, unknown knowns and unknowns unknowns).

\hypertarget{papers-summary}{%
\section{Papers summary}\label{papers-summary}}

\hypertarget{requirements-elicitation-towards-the-unknown-unknowns-sutcliffe2013requirements}{%
\subsection{Requirements elicitation: Towards the Unknown Unknowns
{[}2{]}}\label{requirements-elicitation-towards-the-unknown-unknowns-sutcliffe2013requirements}}

@@

@@

I need some conclusions

\hypertarget{what-ill-do}{%
\section{What i'll do}\label{what-ill-do}}

Explain tacit knowledge explain domain knowledge Explain acceptance
unclarity Explain Dung's framework Explain ASPIC+ Inconsistencies It's
highly influenced by the domain knowledge of the analyst

\newpage

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-lauesen2001softwarereq}{}%
{[}1{]} S. Lauesen, \emph{Software requirements: Styles and techniques},
1st ed. Pearson Education, 2001.

\leavevmode\hypertarget{ref-sutcliffe2013requirements}{}%
{[}2{]} A. Sutcliffe and P. Sawyer, ``Requirements elicitation: Towards
the unknown unknowns,'' in \emph{Requirements engineering conference
(re), 2013 21st ieee international}, 2013, pp. 92--104.

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
Interviews are the most common technique in requirements elicitation.
However, the presence of tacit knowledge have an important influence on
interviews success. In this paper, we describe a tacit knowledge
classification. Then we make use of a theoretical framework and examples
to detect and minimize the effects of tacit knowledge. Finally, we
analyze how likely is to have a sucessful elicitation interviews based
on the tacit knowledge classification.

% lncs keyword extension 
\keywords{interview, tacit knowledge, elicitation}

@@

Requirements engineering is the subset of systems engineering concerned
with discovering, developing, tracing, analyzing, qualifying,
communicating and managing requirements that define the system at
succesive levels of abstraction {[}1{]}. The first step of requirements
engineering is requirements elicitation which is defined as the process
of finding and formulation requirements {[}2{]}, and this process has
many barriers due to stakeholders are not able to express their needs,
explain what they do and why, conflicting demands, or new demands once
other are met, just to mention some examples.

One of the most used techiques to elict requirements is open interviews,
and also is considered the most effective way to transfer domain
knowledge {[}3{]}. However, the success of interviews depends on mainly
two factors, analyst set of interviewing skills and stakeholders domain
knowledge; nonetheless, statistically analyst domain knowledge is
important but not as relevant as the other two{[}4{]}. Therefore,
analyst should make use of tools and techniques to detect and elicit
tacit knowledge form stakeholders. Tacit knowledge is in requirements
engineering is defined as the knowledge that a stakeholders has, but
does not pass to the requirements analyst {[}5{]}.

In this paper we describe a classification of tacit knowledge in
elicitation interviews based on {[}6{]}. Then we apply the theoretical
framework described in {[}3{]} in examples to show how to deal with
tacit knowledge. The examples were selected in order to match the each
scenario of the classification. Finally, we use the result from {[}4{]}
to identify in which scenario is most likely to perform a succesful
interview.

The remainder paper is structured as follows. In section 2 we provide a
summary of the papers used to write this paper. In section 3 we present
our approach. Finally, in section 4, we present our conclusions.

\hypertarget{background}{%
\section{Background}\label{background}}

\hypertarget{requirements-elicitation-towards-the-unknown-unknowns-sutcliffe2013requirements}{%
\subsection{Requirements elicitation: Towards the Unknown Unknowns
{[}6{]}}\label{requirements-elicitation-towards-the-unknown-unknowns-sutcliffe2013requirements}}

@@

\hypertarget{tacit-knowledge-in-elicitation-interviews}{%
\section{Tacit knowledge in elicitation
interviews}\label{tacit-knowledge-in-elicitation-interviews}}

\hypertarget{types-of-tacit-knowledge}{%
\subsection{Types of tacit knowledge}\label{types-of-tacit-knowledge}}

Many analyst consider interviews the most important elicitation
technique, and usually elicitation process starts with interviewing the
stakeholders. Interviews allow analysts to check their understanding
about the problem domain immediately and ask for clarifications.
Moreover, this technique is versatile in the sense of it is possible
that new and unexpected issues come up and they can be attacked at that
moment.

However, elicit tacit knowledge in interviews is still a hard task to
do. This tacit knowledge can be classified in four groups as describe in
{[}6{]}. The \textbf{known knowns}, \textbf{known unknowns},
\textbf{unknown knowns} and \textbf{unknown unknowns}. The known knowns
is the knowledge that is documented, expressible, and relevant to the
system. In order words, is the scenario in which it is possible to
elicit since the beginning all the requirements, there is no tacit
knowledge. The known unknowns is the knowledge that cannot be
expressible because the stakeholders are not aware of their lack of
domain knowledge, their might forget it. In this case analyst are aware
of the domain knowledge and therefore, their job is to challenge
assumptions or implications. The unknown knowns is the knowledge that
stakeholders hold but it is not documented by some reason. Thus,
analysts should use their interviewing skill to elicit when they spot
any glimpse of that knowledge. The unknown unknowns is the knowledge
that neither the analysts nor stakeholders are aware.

\hypertarget{how-to-deal-with-tacit-knowledge}{%
\subsection{How to deal with tacit
knowledge}\label{how-to-deal-with-tacit-knowledge}}

In the last section we present how to use a theoretical framework based
on arguments and attacks to addresed the different levels of tacit
knowledge. In this section we will compare in which scenario of tacit
knowledge the elicitation interview would be more effective based on
Aranda et al.~work {[}4{]} about the effect of domain knowledge on
elicitation process.\\
Effectiveness is described in {[}4{]} as the total percentage of problem
domain elements identified compared to a benchmark. However, since we
have no accesse to any requirement data, we will use the conclusions of
{[}4{]} to compare the different scenarios of tacit knowledge (known
unknowns, unknown knowns and unknowns unknowns).

@@

Elicitation interviews is not an easy task. Like in any intensive oral
communication there are missunderstandings related to tacit knowledge.
In our work we focus on analysing the different levels of how tacit
knowledge{[}6{]} would affect the effectiveness of elicitation
interviews. Moreover, we use the theoretical framework described in
{[}3{]} to indentify and manage tacit knowledge during interviews. And
finally, we analyze based on the results of {[}4{]} in which scenario of
tacit knowledge it is more likely to have a sucessful elictation
interview.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-dick2017requirements}{}%
{[}1{]} J. Dick, E. Hull, and K. Jackson, \emph{Requirements
engineering}. Springer International Publishing, 2017.

\leavevmode\hypertarget{ref-lauesen2001softwarereq}{}%
{[}2{]} S. Lauesen, \emph{Software requirements: Styles and techniques},
1st ed. Pearson Education, 2001.

@@

\leavevmode\hypertarget{ref-ferrari2015ambiguity}{}%
{[}5{]} A. Ferrari, P. Spoletini, and S. Gnesi, ``Ambiguity as a
resource to disclose tacit knowledge,'' in \emph{Requirements
engineering conference (re), 2015 ieee 23rd international}, 2015, pp.
26--35.

\leavevmode\hypertarget{ref-sutcliffe2013requirements}{}%
{[}6{]} A. Sutcliffe and P. Sawyer, ``Requirements elicitation: Towards
the unknown unknowns,'' in \emph{Requirements engineering conference
(re), 2013 21st ieee international}, 2013, pp. 92--104.
